### 2020-09-09 Analysis/Code/Paper.Rmd
minor changes

\noindent $disc_{it} = \mathds{1}\{Discount_{it} > 0\}$ is a dummy measuring if the game is on a discount or not, $X_{it}$ is a set of control variables that includes log proximities to positive and negative transitions, log review count, review bin dummies, and age; $f_i$ is a set of game-level fixed effects, and $\tau_t$ is a set of day of the week effects and sample week time effects. These time effects are especially important to include in the regressions with discounting variables on the left hand side, because Steam's curated discounts all start on predetermined days of the week, and seasonal sales affect a big number of games at the same time, as depicted in Figure \ref{seasonalSalesPeriods}. We expect $\beta^+$ to be positive, but, when it comes to $\beta^-$, any sign could be rationalized. A positive sign on  $\beta^-$ would serve as evidence that firms use discounting in order to escape from slumps in their reviews bins, while a negative sign would indicate that, on the contrary, firms on the verge of a bad transition become more prudent with their discounts, trying to not instigate extra purchasing/reviewing activity.

@@

The results in Table \ref{potentialTransitionsResults} unequivocally support the hypothesis that proximity to a review bin upgrade increases firms' willingness to run a price promotion. Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to have a discount\footnote{The corresponding number for the games in the treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg1$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount. The uncertainty about the sign and the significance of the proximity to a potential negative transition is resolved in favor of the prudent approach on the firms' side: the results suggest that firms under a risk of deteriorating their review label are `r -round(100*(reg3$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`-`r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% less likely to go on a discount, albeit the effect is only present in two out of three specifications.

@@

table <- texreg(res,
                stars = c(0.01, 0.05, 0.1),
                digits = 3,
                custom.model.names = c("(1)", "(2)", "(3"),
                reorder.coef = c(1, 2, 6, 7, 8, 9, 10, 11, 5, 12, 3, 4, 13, 14),
                caption = "Estimates of the Demand Parameters",
                caption.above = T,
                label = "demandEstimates")

@@

# calculate s.e.
id.matrix <- matrix(c(1,0,0,1), nrow=2)
for (id in revs[, ID]){
   sums <- panel[ID==id, .(disc, lam)][, sum(lam), by = disc]

@@

   Hpos <- matND/revs[ID==id, rhoPosND] + matD/revs[ID==id, rhoPosD]
   HposInv <- solve(Hpos, id.matrix)

   Hneg <- matND/revs[ID==id, rhoNegND] + matD/revs[ID==id, rhoNegD]
   HnegInv <- solve(Hpos, id.matrix)

@@

# label all games with significant rho_1^+
revs[, posSignif := abs((rhoPosD-rhoPosND)/rhoPos1se) >= 1.96]
revs[, negSignif := abs((rhoNegD-rhoNegND)/rhoNeg1se) >= 1.96]
rm(Hpos, Hneg, HnegInv, HposInv)
```

```{r like-rates, include = F}
p1 <- ggplot(data = revs[, .(x = rhoPosD-rhoPosND)][x>=-0.5& x<=2,]) +
  ggtitle("Discount Contribution to Likes") +
  geom_histogram(mapping = aes(x = x, y = ..density..),
                 color = "black",
                 position = "identity",
                 boundary = 0,
                 alpha = 0.9,
                 binwidth = 0.1,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x),
                 color = "black",
                 position = "identity",
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Change in Like Rates",
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL,
                     breaks = c(0, 1, 2),
                     minor_breaks = NULL) +
  my.theme() +
  coord_cartesian(xlim = c(-0.5, 2))

p2 <- ggplot(data = revs[, .(x = rhoNegD-rhoNegND)][x>=-0.5& x<=2,]) +
  ggtitle("Discount Contribution to Dislikes") +
  geom_histogram(mapping = aes(x = x, y = ..density..),
                 color = "black",
                 position = "identity",
                 boundary = 0,
                 binwidth = 0.025,
                 alpha = 0.9,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x),
                 color = "black",
                 position = "identity",
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Change in Dislike Rates",
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL,
                     minor_breaks = NULL) +
  my.theme() +
  coord_cartesian(xlim = c(-0.5, 2))

ggarrange(p1, p2, nrow=2, align = "v")
```

```{r fig.cap='\\label{likeRatesPlot} Distributions of $\\rho_{1i}^+$ and $\\rho_{1i}^-$'}
ggarrange(p1, p2, nrow=1, align = "h")
```

@@

```{r results = 'asis', warning = FALSE}
# remove 1% with the highest values of rho_1+ (<=2)
# and only keep significant coefficients
panel <- merge(panel, revs[, .(ID, rho1 = rhoPosD - rhoPosND, rhoPosD, rhoNegD)])

@@

reg1 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
               mPositive + realPositive + vPositive + age + young + day + week,
           data = panel[rho1 <= 2 & rho1 >= -0.5 
                        # ID %in% revs[negSignif == T | posSignif == T, ID], 
                        ],
           model = "pooling")
cov<-vcovHC(reg1, method="white1")
se1 <- sqrt(diag(cov))

reg2 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
               mPositive + realPositive + vPositive + age + young + day + week,
           data = panel[rho1 <= 2 & rho1 >= -0.5
                        # ID %in% revs[negSignif == T | posSignif == T, ID], 
                        ],
           model = "within")
cov<-vcovHC(reg2, method = "white1")
se2 <- sqrt(diag(cov))

star.out<-stargazer(reg1, reg2,
                    label = "rhoTransDiscReg",
                    header = FALSE,
                    title = "Discounts Before Potential Transitions And Firm Heterogeneity",
                    se=list(se1, se2),
                    dep.var.labels = c("$\\mathbb{P}(Discount)$"),
                    # column.labels=c("OLS", "Interaction", "FE", "FE: no $\\rho_{1i}^+$"),
                    model.numbers = F,
                    omit = c("tWODisc", "reviews", "noScore", "realPositive", 
                             "mPositive", "vPositive", "age", "young", "Constant",
                             "score", "day", "week", "needPosDays", "needNegDays"),
                    #covariate.labels = ,
                    order = c("rho1"),
                    omit.stat=c("f","adj.rsq","ser"),
                    no.space=T)
```

@@

\newpage
## Response Of Reviews and Score to Discounts
Table \ref{reviewLag} presents the results of estimating
$$y_{it} \sim \sum_{l = 0}^{7} \mathds{1}(\text{Disc. } l \text{ days ago})
+ Controls_{it} +  f_i + \tau_t + u_{it}$$
\noindent for $y_{it}$ being the number of new reviews for game $i$ on day $t$ and game $i$'s 
review score. I use all the same controls as usual: review bin, score (in the first regression),
log reviews, age, dummy for being less than 14 days old.

@@

reg2 <- plm(score~ discNew + discNewLag + discNewLag2 + discNewLag3 + discNewLag4 +
                           discNewLag5 + discNewLag6 + discNewLag7 +
                           negative + mPositive + realPositive + vPositive + ovPositive +
                           log(reviews + 1) + age + young + day + week,
                           data = panel, model = "within")
cov<-vcovHC(reg2, method="white1")
se2 <- sqrt(diag(cov))

star.out <- stargazer(reg1, reg2, 
             label = "reviewLag",
             table.placement = "hp",
             header = FALSE,
             title = "Changes in Review Flows and Score After a Discount",
             se=list(se1),
             dep.var.labels = c("New Reviews", "Score (0-100)"),
             covariate.labels = c("Discount 0 Days Ago", "Discount 1 Day Ago",
                                  "Discount 2 Days Ago", "Discount 3 Days Ago",
                                  "Discount 4 Days Ago", "Discount 5 Days Ago",
                                  "Discount 6 Days Ago", "Discount 7 Days Ago"),
             model.numbers = F,
             omit = c("day","week","negative","mPositive","realPositive",
                      "vPositive", "ovPositive", "reviews", "score", "age", "young"),
             omit.stat=c("f","adj.rsq","ser"),
             no.space=T)
panel[, discNewLag2:=NULL][, discNewLag3:=NULL][, discNewLag4:=NULL][, discNewLag5:=NULL]
panel[, discNewLag6:=NULL][, discNewLag7:=NULL][, new.reviews:=NULL]
```

>>>>

\noindent $disc_{it} = \mathds{1}\{Discount_{it} > 0\}$ is a dummy measuring if the game is on a discount or not, $X_{it}$ is a set of control variables that includes log proximities to positive and negative transitions, log review count, score, review bin dummies, and age; $f_i$ is a set of game-level fixed effects, and $\tau_t$ is a set of day of the week effects and sample week time effects. These time effects are especially important to include in the regressions with discounting variables on the left hand side, because Steam's curated discounts all start on predetermined days of the week, and seasonal sales affect a big number of games at the same time, as depicted in Figure \ref{seasonalSalesPeriods}. We expect $\beta^+$ to be positive, but, when it comes to $\beta^-$, any sign could be rationalized. A positive sign on  $\beta^-$ would serve as evidence that firms use discounting in order to escape from slumps in their reviews bins, while a negative sign would indicate that, on the contrary, firms on the verge of a bad transition become more prudent with their discounts, trying to not instigate extra purchasing/reviewing activity.

@@

The results in Table \ref{potentialTransitionsResults} unequivocally support the hypothesis that proximity to a review bin upgrade increases firms' willingness to run a price promotion. Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to have a discount\footnote{The corresponding number for the games in the treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg1$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount. The uncertainty about the sign and the significance of the proximity to a potential negative transition is resolved in favor of the prudent approach on the firms' side: the results suggest that firms under a risk of deteriorating their review label are `r -round(100*(reg3$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`-`r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% less likely to go on a discount, albeit the effect is only significant at 1\% level in two out of three specifications.

@@

table <- texreg(res,
                stars = c(0.01, 0.05, 0.1),
                digits = 3,
                custom.model.names = c("(1)", "(2)", "(3)"),
                reorder.coef = c(1, 2, 6, 7, 8, 9, 10, 11, 5, 12, 3, 4, 13, 14),
                caption = "Estimates of the Demand Parameters",
                caption.above = T,
                label = "demandEstimates")

@@

# calculate s.e.
id.matrix <- matrix(c(1,0,0,1), nrow=2)
for (id in revs[, ID]){
   sums <- panel[ID==id, .(disc, lam)][, sum(lam), by=disc][!is.na(disc),]

@@

   Hpos <- matND/revs[ID==id, rhoPosND] + matD/revs[ID==id, rhoPosD]
   HposInv <- tryCatch(solve(Hpos, id.matrix),
                       error = function(x){return(matrix(rep(NA,4), 
                                                         nrow = 2))})

   Hneg <- matND/revs[ID==id, rhoNegND] + matD/revs[ID==id, rhoNegD]
   HnegInv <- tryCatch(solve(Hneg, id.matrix),
                       error = function(x){return(matrix(rep(NA,4), 
                                                         nrow = 2))})

@@

# label all games with significant rho_1^+
revs[, posSignif := abs((rhoPosD-rhoPosND)/rhoPos1se) >= 1.96]
revs[, negSignif := abs((rhoNegD-rhoNegND)/rhoNeg1se) >= 1.96]

# score off discount and score on discount
revs[, scoreND := rhoPosND/(rhoPosND+rhoNegND)]
revs[, scoreD := rhoPosD/(rhoPosD+rhoNegD)]
revs[, score.dif := scoreD - scoreND]

rm(Hpos, Hneg, HnegInv, HposInv)
```

```{r}
# Game by game test whether reviews during a discount are more positive 
# (in the score sense) than those off discount
f <- panel[!is.na(disc), .(disc, l = c(pReviews[1], diff(pReviews)), d = c(nReviews[1], diff(nReviews))), by = ID][, .(n1 = sum(l), n0 = sum(d)), keyby = c("ID", "disc")]

test <- f[,  .(p.val = tryCatch(t.test(c(rep(1, n1[1]), rep(0, n0[1])),
         c(rep(1, n1[2]), rep(0, n0[2])),
         alternative = "less")$p.value,
         error = function(x){-1})), by = ID]
test[p.val ==-1, p.val := NA]
discIDs <- test[p.val <=0.05, ID]
panel[, scoreIsBiggerDisc := (ID %in% test[p.val <= 0.05, ID])]

test <- f[,  .(p.val = tryCatch(t.test(c(rep(1, n1[1]), rep(0, n0[1])),
         c(rep(1, n1[2]), rep(0, n0[2])),
         alternative = "greater")$p.value,
         error = function(x){-1})), by = ID]
test[p.val ==-1, p.val := NA]
discIDs <- test[p.val <=0.05, ID]
panel[, scoreIsLessDisc := (ID %in% test[p.val <= 0.05, ID])]
```

```{r fig.cap='\\label{likeRatesPlot} Distributions of $\\rho_{1i}^+$ and $\\rho_{1i}^-$'}
p1 <- ggplot(data = revs[, .(x = rhoPosD-rhoPosND)][x>=-0.5& x<=2,]) +
  geom_histogram(mapping = aes(x = x, y = ..density..),
                 color = "black",
                 position = "identity",
                 boundary = 0,
                 alpha = 0.9,
                 binwidth = 0.1,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x),
                 color = "black",
                 position = "identity",
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Change in Like Rates",
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL,
                     breaks = c(0, 1, 2),
                     minor_breaks = NULL) +
  my.theme() +
  coord_cartesian(xlim = c(-0.5, 2))

p2 <- ggplot(data = revs[, .(x = rhoNegD-rhoNegND)][x>=-0.5& x<=2,]) +
  geom_histogram(mapping = aes(x = x, y = ..density..),
                 color = "black",
                 position = "identity",
                 boundary = 0,
                 binwidth = 0.025,
                 alpha = 0.9,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x),
                 color = "black",
                 position = "identity",
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Change in Dislike Rates",
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL,
                     minor_breaks = NULL) +
  my.theme() +
  coord_cartesian(xlim = c(-0.5, 2))

```{r like-rates, fig.width = 8, fig.height = 6, include = FALSE}
ggarrange(p1, p2, nrow=2, align = "v")
```

@@

```{r results = 'asis', warning = FALSE}
# remove 1% with the highest values of rho_1+ (<=2)
# and only keep significant coefficients
panel <- merge(panel, revs[, .(ID, rho1 = rhoPosD - rhoPosND, score.dif)])

@@

reg1 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
               mPositive + realPositive + vPositive + age + young + day + week,
           data = panel[rho1 <= 2 & rho1 >= -0.5,],
           model = "pooling")
cov<-vcovHC(reg1, method="white1")
se1 <- sqrt(diag(cov))

reg2 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
               mPositive + realPositive + vPositive + age + young + day + week,
           data = panel[rho1 <= 2 & rho1 >= -0.5 & 
                        ID %in% revs[negSignif == T | posSignif == T, ID], 
                        ],
           model = "pooling")
cov<-vcovHC(reg2, method="white1")
se2 <- sqrt(diag(cov))

reg3 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
               mPositive + realPositive + vPositive + age + young + day + week,
           data = panel[rho1 <= 2 & rho1 >= -0.5
                        # ID %in% revs[negSignif == T | posSignif == T, ID], 
                        ],
           model = "within")
cov<-vcovHC(reg3, method = "white1")
se3 <- sqrt(diag(cov))

reg4 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
               mPositive + realPositive + vPositive + age + young + day + week,
           data = panel[rho1 <= 2 & rho1 >= -0.5 & 
                        ID %in% revs[negSignif == T | posSignif == T, ID], 
                        ],
           model = "within")
cov<-vcovHC(reg4, method = "white1")
se4 <- sqrt(diag(cov))

star.out<-stargazer(reg1, reg2, reg3, reg4,
                    label = "rhoTransDiscReg",
                    header = FALSE,
                    title = "Discounts Before Potential Transitions And Firm Heterogeneity",
                    se=list(se1, se2, se3, se4),
                    dep.var.labels = c("$\\mathbb{P}(Discount)$"),
                    column.labels=c("OLS", "OLS:Signif", "FE", "FE:Signif"),
                    model.numbers = F,
                    omit = c("tWODisc", "reviews", "noScore", "realPositive", 
                             "mPositive", "vPositive", "age", "young", "Constant",
                             "score", "day", "week", "needPosDays", "needNegDays"),
                    covariate.labels = c("$\\rho_1^+$",
                                         "$\\rho_1^+ \\times$ Pos. Tr.",
                                         "$\\rho_1^+ \\times$ Neg. Tr.",
                                         "Pos. Tr.", "Neg. Tr."),
                    order = c("rho1"),
                    omit.stat=c("f","adj.rsq","ser"),
                    no.space=T)
```

@@

\newpage
## Response Of Reviews and Score to Discounts
Table \ref{reviewLag} presents the results of estimating
$$y_{it} \sim \sum_{l = 0}^{7} \mathds{1}(\text{Disc. } l \text{ days ago})
+ Controls_{it} +  f_i + \tau_t + u_{it}$$
\noindent for $y_{it}$ being the number of new reviews for game $i$ on day $t$, the ratio of new reviews to the average speed of review arrival, and game $i$'s 
review score. I use all the same controls as usual: review bin, score (in the first regression),
log reviews, age, dummy for being less than 14 days old.

@@

reg2 <- plm(I(new.reviews/(pRevRate+nRevRate)) ~ discNew + discNewLag + discNewLag2 + discNewLag3 + discNewLag4 +
                          discNewLag5 + discNewLag6 + discNewLag7 +
                          negative + mPositive + realPositive + vPositive + ovPositive + 
                          score + log(reviews + 1) + age + young + day + week,
                          data = panel, model = "within")
cov<-vcovHC(reg2, method="white1")
se2 <- sqrt(diag(cov))

reg3 <- plm(score ~ discNew + discNewLag + discNewLag2 + discNewLag3 + discNewLag4 +
                           discNewLag5 + discNewLag6 + discNewLag7 +
                           negative + mPositive + realPositive + vPositive + ovPositive +
                           log(reviews + 1) + age + young + day + week,
                           data = panel, model = "within")
cov<-vcovHC(reg3, method="white1")
se3 <- sqrt(diag(cov))

star.out <- stargazer(reg1, reg2, reg3, 
             label = "reviewLag",
             table.placement = "hp",
             header = FALSE,
             title = "Changes in Review Flows and Score After a Discount",
             se=list(se1, se2, se3),
             dep.var.labels = c("New Reviews", "New Reviews \\%", "Score (0-100)"),
             covariate.labels = c("Discount 0 Days Ago", "Discount 1 Day Ago",
                                  "Discount 2 Days Ago", "Discount 3 Days Ago",
                                  "Discount 4 Days Ago", "Discount 5 Days Ago",
                                  "Discount 6 Days Ago", "Discount 7 Days Ago"),
             model.numbers = F,
             omit = c("day","week","negative","mPositive","realPositive",
                      "vPositive", "ovPositive", "reviews", "score", "age", "young"),
             omit.stat=c("f","adj.rsq","ser"),
             no.space=T)
panel[, discNewLag2:=NULL][, discNewLag3:=NULL][, discNewLag4:=NULL][, discNewLag5:=NULL]
panel[, discNewLag6:=NULL][, discNewLag7:=NULL][, new.reviews:=NULL]
```
